---
title: "Homework 7"
format: html
editor: visual
---

## Exercise 1

a\. Be aware of labels, as bar plots usually take up a lot of horizontal space. In order to fix this probelm, you could use rotated labels (not the nest option) or swap the x and y-axis.

b\. Wilke advises not to use bar charts when the nature of the data does not match with what a bar chart displays. A lot of times, bar charts are easier to create; however, it obscures the data and the story it is supposed to display.

c\. Dot plots, heat maps, and box plots.

d\. Stacked bars are best for showing part-to-whole relationships while dodged bars are best for showing relationships across groups.

e\.

```{r}
library(vegabrite)

vl_chart() |>
  vl_mark_bar() |>
  vl_encode_x ("amount:Q", title = "Weekend Gross") |>
  vl_encode_y("title:N", title = "") |>
  vl_add_data(url="https://calvin-data304.netlify.app/data/cow-movies.csv")
```

f\.

```{r}
vl_chart() |>
  vl_mark_bar() |>
  vl_encode_x("race:N") |>
  vl_encode_y("median_in:Q") |>
  vl_encode_color("age:O") |>
  vl_add_data(url = "https://calvin-data304.netlify.app/data/cow-income.csv")
```

```{r}
vl_chart() |>
  vl_mark_bar() |>
  vl_encode_x("age:N") |>
  vl_encode_y("median_in:Q") |>
  vl_facet("race:N") |>
  vl_add_data(url="https://calvin-data304.netlify.app/data/cow-income.csv")
```

g\.

```{r}
vl_chart() |>
  vl_mark_point() |>
  vl_encode_x("lifeExp:Q") |>
  vl_encode_y("country:N") |>
  vl_add_data(url="https://calvin-data304.netlify.app/data/cow-gapminder.csv")
```

## Exercise 2

b\.

## Exercise 3

a\. Mapping data values onto colors rather than mapping them onto positions.

b\.

```{r}
vl_chart() |>
  vl_mark_rect() |>
  vl_encode_x("year:O") |>
  vl_encode_y("country:N") |>
  vl_encode_color("users:Q") |>
  vl_add_data(url="https://calvin-data304.netlify.app/data/cow-internet2.csv")
```

c\.

d\.
