---
title: "Portfolio"
format: html
editor: visual
---

## Exercise 1

a\. I like Daniel's graphic that compares twins because I think it displays the data very well and he utilizes color very well.

b\. I am not a huge fan of Lily's graphic that compares twins because the scaling is way off, so you cannot tell exactly what it is supposed to be showing.

c\.

```{r}
library(vegabrite)

vl_chart(title=) |>
  vl_mark_point() |>
  vl_encode_x("twin:N", title="Genetic Share") |>
  vl_encode_y("genetic share:Q", title="Twin Pairs") |>
  vl_encode_color("region:N") |>
  vl_add_data(url="https://calvin-data304.netlify.app/data/twins-genetics-long.json")
```

This graphic shows the genetic share between all six sets of twins and how that compares to the region the twins are from.

```{r}
vl_chart() |>
  vl_mark_point() |>
  vl_encode_x("genetic share:Q") |>
  vl_encode_y("kit:N") |>
  vl_add_data(url="https://calvin-data304.netlify.app/data/twins-genetics-long.json")
```

This graphic shows the genetic share between twins based on the kit that was used to calculate the genetic share.

## Exercise 2

```{r}
base <- vl_chart() |>
  vl_mark_line(point=TRUE) |>
  vl_encode_x("Date:O") |>
  vl_add_data(url="https://calvin-data304.netlify.app/data/swd-lets-practice-ex-2-13.json")

completion <- base |>
  vl_encode_y("Completion Rate:Q") |>
  vl_encode_color(datum = "Completion", type = "nominal")

response <- 
  base |>
  vl_encode_y("Response Rate:Q") |>
  vl_encode_color(datum = "Response", type = "nominal")

completion + response
```

## Exercise 3

a\.

```{r}
data <- "/mnt/data/tanzania_dhs_survey_split.json"
```

b\.

```{r}
vl_chart() |>
  vl_mark_line(point=TRUE) |>
  vl_encode_x("Modern_Contraception_Use:Q") |>
  vl_encode_y("Unmet_Need_For_Family_Planning:Q") |>
  vl_encode_color("Total_Fertility_Rate:Q") |>
  vl_facet("DHS_Survey_Year:T") |>
  vl_add_data(url="/mnt/data/tanzania_dhs_survey_split.json")
```

## Exercise 5

a\. I encoded a color channel in almost all of the graphics I created

b\. I layered my graphic for exercise 2 in order to get both completion and response rates.

c\. I faceted my graphic in exercise 3 for each year.

d\. I also used concatenation for exercise 2 where I layered.

e\. I changed the settings for exercise 2.

## Exercise 6

a\. In all of my graphics, I personalized the titles and sorted things differently.

b\. In exercise 2, I made sure the colors were pleasing for the vieweer, which was discussed in Wilke Chapter 4.
